---
title: "Assignment 3 : Data Visualization (incarceration)"
author: "Angela Lin"
date: "2/22/2022"
output: html_document
---

```{r setup, include=FALSE}
library("ggplot2")
library("dplyr")
knitr::opts_chunk$set(echo = TRUE)
```

### 1. Introduction

In this data visualization, I want to look at the differences in incarceration number by state, race, gender, and age. I choose to analyze the population in jail of different states and races. Also, I want to compare the difference in population in jail between males and females, teenagers and adults.

### 2. Summary Information

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("../source/analysis.R")
summary_info
```

### 3. Trends over time chart

This chart helps to demonstrate how the population in jail of different races develop over time. In the trends over time chart, I use points to represent the population in each year and lines in the chart to display the overall trend.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("../source/analysis.R")
race_pop_over_time()
```

### 4. Variable comparison chart

This chart helps to demonstrate how the population in jail develops between the two genders. In the chart, I use points to represent the population each year and lines to compare the development of the female and male populations in jail.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("../source/analysis.R")
gender_pop_over_time()
```

### 5. Map
This map shows the population in jail distributed in Washington counties. I use the different sizes of circles to demonstrate the differences in population in counties. 
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("../source/analysis.R")

```
